\documentclass{resume}

% bibliography with multiple entries
\usepackage{multibib}
\newcites{papers}{Selected Publications}
\newcites{talks}{Selected Talks}

\usepackage{xpatch}
\makeatletter
\newcommand\removebibheader
  {\xpatchcmd\std@thebibliography
    {\section*{\refname}%
     \@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}%
    }{}{}{}%
  }
\makeatother

\usepackage{etoolbox}
\BeforeBeginEnvironment{thebibliography}{%
  \let\origsection\section% save original definition of \section
  \let\section\subsection%  make \section behave like \subsection
}
\AfterEndEnvironment{thebibliography}{%
  \let\section\origsection% restore original definition of \section
}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}

\newcommand{\CC}{C\nolinebreak\hspace{-.05em}\raisebox{.4ex}{\tiny\bf +}\nolinebreak\hspace{-.10em}\raisebox{.4ex}{\tiny\bf +}}
\def\CC{{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}}

\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\input{env}
\fancyhead{}
\fancyfoot{}
\rfoot{\footnotesize \href{{https://jmrolsson.github.io/cv/JoakimOlssonCV.pdf}}{\faLink~Joakim Olsson's CV} (version: \href{https://github.com/jmrolsson/cv/tree/\COMMITHASH}{\COMMITHASH})}

\name{\href{http://jmrolsson.com}{Joakim Olsson}}
\address{University of California, Irvine \hfill CERN CH - B\^atiment 104-R-C29}
\address{4129 Frederick Reines Hall, Irvine CA 92697\hfill Gen\`eve, Switzerland}
\address{\href{mailto:olsson@uci.edu}{\faicon{envelope}~olsson@uci.edu} \hfill \href{https://www.twitter.com/jmrolsson}{\faicon{twitter}} \href{https://www.linkedin.com/in/jmrolsson}{\faicon{linkedin}} \href{https://www.github.com/jmrolsson}{\faicon{github}~@jmrolsson} \href{http://jmrolsson.com}{\faicon{link}~jmrolsson.com}}
\address{\href{tel:+13127809260}{\faicon{phone}~+1 (312) 780-9260} \hfill \href{https://orcid.org/0000-0003-4154-8139}{\faicon{key}~ORCID: 0000-0003-4154-8139}\vspace{1.0em}}

\linespread{1.0}

\begin{document}

%----------------------------------------------------------------------------------------
% RESEARCH INTERESTS	
%----------------------------------------------------------------------------------------

\begin{rsection}{Research Interests}
  \begin{rlist}
    \item Experimental high energy physics: searches for BSM physics, SM/Higgs measurements, jets and jet substructure, hardware/firmware development, and machine learning applications
    \item Experimental astrophysics and cosmology
    \item Machine learning 
  \end{rlist}
\end{rsection}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\begin{rsection}{Education}

  \rsubsectiontitle{University of Chicago}{Chicago, IL}{Ph.D. Physics, Advisor: David W. Miller}{2012 -- 2018}\\
  \rsubsubsectiontitle{M.S. Physics}{2014}
  \vspace{-0.2em}
  \item Dissertation: \\{\em Searching for Supersymmetry in Fully Hadronic Final States with the ATLAS Experiment}

%------------------------------------------------

  \rsubsectiontitle{Chalmers University of Technology}{Gothenburg, Sweden}{M.S. Fundamental Physics}{2010 -- 2012}
  \vspace{-0.2em}
  \item Thesis: {\em Simulation of physics beyond the Standard Model with an extra $U(1)'$ gauge boson}

%------------------------------------------------

  \rsubsectiontitle{Tohoku University}{Sendai, Japan}{Exchange student: full time research in lab, courses in physics and Japanese}{2009 -- 2010}

%------------------------------------------------

  \rsubsectiontitle{Chalmers University of Technology}{Gothenburg, Sweden}{B.S. Engineering Physics}{2006 -- 2009}
  \vspace{-0.2em}
  \item Thesis: {\em Autonomous guidance system for a model airplane}

\end{rsection}

%----------------------------------------------------------------------------------------
%	RESEARCH
%----------------------------------------------------------------------------------------

\begin{rsection}{Relevant Experience}

  \begin{rsubsection}{University of California, Irvine}{Irvine, CA}{Postdoctoral Scholar}{October 2018 -- Present}
  \item Leading a team as analysis contact for an ATLAS search with pair production of two Higgs bosons decaying into final states with quarks and leptons.
  \item Working on algorithm and firmware development for the Phase-II upgrade of the ATLAS Muon Spectrometer.
  \item Deploying machine learning techniques to improve analysis sensitivity, and exploring the application of neural networks for fast inference on FPGAs in the trigger. 
  \end{rsubsection}

  \begin{rsubsection}{CERN (European Organization for Nuclear Research)}{Geneva, Switzerland}{Ph.D. Student, UChicago/ATLAS Experiment}{September 2012 -- August 2018}
  \item Lead analyser in two searches for supersymmetry with the ATLAS detector, an 8 TeV search for R-parity-violating stops \cite{RPVstop2016}, and a 13 TeV search for direct production of a chargino and a neutralino decaying via $Wh$ to fully hadronic final states (thesis analysis, paper in-progress). I was responsible for all aspects of the analysis, including private sample production for sensitivity studies, developing the strategy to suppress background, data/MC comparisons, systematics, HistFitter limit setting, helping to maintaining the analysis framework, editing supporting note, etc.
  \item Analyzed data and helped to prepare material for an ATLAS Run I search for R-parity-violating supersymmetric gluino pair-production with signatures based on high jet multiplicities \cite{Multijet2015}. 
  \item Measured the ATLAS calorimeter response to single isolated charged hadrons (E/p) during LHC Run II data taking, focusing primarily on the ATLAS Tile Calorimeter (TileCal).
  \item Developed software, analyzed data, supervised students, and took on a leading role during four test beam runs at CERN for the ATLAS TileCal High Luminosity LHC upgrade.
  \item Oversaw the trigger and beam line elements during TileCal test beam activities at CERN. 
  \item Led a small team responsible for data quality of TileCal (Tile DQ Team Leader).
  \item Supervised students working in the University of Chicago ATLAS group at CERN.
  \item Initiated a project using Deep Neural Networks for ATLAS calorimeter topo-cluster classification.
  \end{rsubsection}

%------------------------------------------------

  \begin{rsubsection}{University of Chicago, Kavli Institute for Cosmological Physics}{Chicago, IL}{Graduate Researcher for the South Pole Telescope (SPT-3g)}{September 2012 -- May 2013}
  \item Measured loss properties in superconducting microstrip transmission lines for coupling the receiving antenna to transition-edge sensor (TES) bolometers in each pixel of the SPT-3g focal plane.
  \item Designed a special ''cold stage'' in Solid Works to minimize heat transfers and reduce noise. 
  \item Worked for Professor \href{https://kicp.uchicago.edu/people/profile/john_carlstrom.html}{John Carlstrom} as part of a course in Advanced Experimental Physics.
  \end{rsubsection}

%------------------------------------------------

  \begin{rsubsection}{CERN (European Organization for Nuclear Research)}{Geneva, Switzerland}{Summer Student in the Caltech CERN CMS Group}{June -- September, 2011}
  \item Studied the impact of spurious signals (''spikes'') in the avalanche photo diodes in the CMS Electromagnetic Calorimeter (ECAL). Authored an CMS Draft Analysis Note: CMS AN-11-481.
  \item Presented my work \href{http://indico.cern.ch/conferenceDisplay.py?confId=135576}{(indico link)} for a large audience at end of the program.
  \item Worked under the supervision of Professor \href{http://www.hep.caltech.edu/~smaria/}{Maria Spiropulu}.
  \end{rsubsection}

%------------------------------------------------

  \begin{rsubsection}{Tohoku University}{Sendai, Japan}{Graduate Researcher in the Solid-State Quantum Transport Group}{October 2009 -- August 2010}
  \item Investigated fundamental characteristics of quantum point contacts; measuring quantized conductance, quantum Hall effect, and resistively-detected Nuclear Magnetic Resonance.
  \item Verified and improved upon research published by the group (PRL 100, 186801), where \textit{e-e} interactions was suggested as an influence for deviations from idealized conductance values.
  \item Improved the accuracy in a transport measurement system by significant noise reduction.
  \item Worked under the supervision of Professor \href{http://quant-trans.org/lab/profile-e.html}{Yoshiro Hirayama}.
  \end{rsubsection}

%------------------------------------------------

  \begin{rsubsection}{University of Florida}{Gainesville, FL}{REU at the Institute for High Energy Physics and Astrophysics}{June -- August, 2009}
  \item Implemented a track reconstruction algorithm for the CMS muon system (using $\CC$ and ROOT). 
  \item Developed trip data analysis software for the CMS Muon Endcap High-Voltage System.
  \item Worked under the supervision of Professor \href{http://www.phys.ufl.edu/~mitselmakher/}{Guenakh Mitselmakher} and Professor \href{http://www.phys.ufl.edu/faculty/furic.shtml}{Ivan Furic}.
  \end{rsubsection}

\end{rsection}

%----------------------------------------------------------------------------------------
%	TEACHING
%----------------------------------------------------------------------------------------

\begin{rsection}{Teaching}

  \rsubsectiontitle{University of Chicago}{Chicago, IL}{}{}\\[0.5em]
  \begin{rsubsubsection}{Graduate Student Teaching Assistant}{2012--2013, 2015, 2017, and 2018}
  \item Demonstrated physics problem solving in discussion sessions of 15-80 students, graded homework, and prepared solutions for courses in classical physics, modern physics, and particle physics.
  \item Supervised experiments and graded technical reports in senior undergraduate physics labs.
  \item Led hands-on electronics laboratory classes for about $20$ students.
  \item Courses: \vspace{-0.1cm}
    \begin{itemize}
      \item PHYS154 -- Modern Physics \hfill Fall 2012 \vspace{-0.2cm}
      \item PHYS185 -- Classical Physics \hfill Winter 2013 \vspace{-0.2cm}
      \item PHYS237 -- Particle Physics \hfill Spring 2013 \vspace{-0.2cm}
      \item PHYS211 -- Advanced Undergraduate Labs \hfill Winter 2015 \vspace{-0.2cm}
      \item PHYS226 -- Electronics \hfill Spring 2015 \vspace{-0.2cm}
      \item PHYS211 -- Advanced Undergraduate Labs \hfill Winter 2017 \vspace{-0.2cm}
      \item PHYS211 -- Advanced Undergraduate Labs \hfill Winter 2018 \vspace{-0.2cm}
    \end{itemize}
  \end{rsubsubsection}

\end{rsection}

%----------------------------------------------------------------------------------------
%	SELECTED PUBLICATIONS
%----------------------------------------------------------------------------------------

\begin{rsection}{Selected Publications}
\bibliographystylepapers{atlasBibStyleWithTitle}
{\removebibheader
\bibliographypapers{papers}
\nocitepapers{*}
}
\end{rsection}

%----------------------------------------------------------------------------------------
%	SELECTED TALKS
%----------------------------------------------------------------------------------------

\begin{rsection}{Selected Talks}
\bibliographystyletalks{atlasBibStyleWithTitle}
{\removebibheader
\bibliographytalks{talks}
\nocitetalks{*}
}
\end{rsection}

%----------------------------------------------------------------------------------------
%	LEADERSHIP 
%----------------------------------------------------------------------------------------

\begin{rsection}{Leadership}

  \begin{rsubsection}{APS Conference for Undergraduate Women in Physics (CUWiP) 2020}{Irvine, CA}{Co-Organizer}{January 17--19, 2020}
  \item Booked speakers and helped with the planning of panel discussions.
  \item Moderated a panel discussion of international physicists.  
  \end{rsubsection}
%------------------------------------------------

  \begin{rsubsection}{Intize.org}{Gothenburg, Sweden}{Math tutor for high-school students}{January 2011 -- June 2012}
  \item Mentored a group of Swedish high school students for a few hours every week.  
  \end{rsubsection}

%------------------------------------------------

  \begin{rsubsection}{CETAC (Chalmers Engineering Trainee Appointment Committee)}{Gothenburg, Sweden}{Appointment Manager and Member of the Board}{2008 -- 2009}
	\item Coordinated trainee appointments for 13 Swedish engineering students at companies in the US and Canada. Despite the 2009 financial crisis, we managed to find paid positions for all members. 
  \end{rsubsection}

%------------------------------------------------

  \begin{rsubsection}{Employment Market Group at the Physics Student Union}{Gothenburg, Sweden}{Chairman}{2007 -- 2008}
		\item Organized a field-trip to CERN for 35 undergraduate students in Engineering Physics at Chalmers.
  \end{rsubsection}

\end{rsection}

%----------------------------------------------------------------------------------------
% OUTREACH	
%----------------------------------------------------------------------------------------

\begin{rsection}{Outreach}
  \textbf{The Museum of Science and Industry, Chicago (March 2013)}\\
  Gave a popular science talk for the general public: The Higgs Boson -- What's the big deal? A HUGE discovery of a TINY particle!\\[0.1cm]
  \textbf{Public Event: Screening of Particle Fever and Discussion Panel (August 2015)}\\
  Moderated a panel discussion of physicists after a movie screening for the general public.
\end{rsection}

%----------------------------------------------------------------------------------------
%	SKILLS/INFO
%----------------------------------------------------------------------------------------

\begin{rsection}{Skills/Info}

  \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Programming & $C$, $\CC$, Python, Bash, Java, JavaScript, Verilog/VHDL \\
    Markup &  JSON, YAML, XML, HTML, CSS, \LaTeXe  \\
    Software/Tools & Unix/Linux, Version Control, \href{https://github.com/jmrolsson}{GitHub}/\href{https://gitlab.cern.ch/jolsson}{GitLab}, Vim (awesome editor), Emacs \\
    & PyTorch, Keras/TensorFlow, scikit-learn, numpy, matplotlib, pandas \\ 
    & ROOT, uproot, Docker, AutoCAD, SolidWorks, LabVIEW \\
    & MATLAB, Mathematica, Adobe Illustrator/Photoshop/InDesign \\ 
    Hardware & Calorimeters, Arduino controllers, NIM crates, FPGA basics, soldering\\ 
    Interpersonal & Project management, leadership, mentorship, public speaking, science outreach\\ 
    Languages & English (fluent), Swedish (native), Japanese (elementary), Spanish (elementary) \\
    Other & US Permanent Resident, Swedish citizenship, Swedish and US driver's license \\
    Hobbies & Skiing, long distance running, powerlifting, hiking, wave surfing \\
    & traveling, reading, coding
  \end{tabular}
\end{rsection}

%----------------------------------------------------------------------------------------
%	HONORS AND AWARDS
%----------------------------------------------------------------------------------------

\begin{rsection}{Honors \& Awards}
  Scholarship for Excellent Academic Achievements, Hvitfeldtska, Gothenburg, Sweden, 2011\\%
  Scholarship for Studies in Japan, Adlerbertska Foundation, Gothenburg, Sweden, 2009\\%
  Scholarship for Studies in Japan, Sweden-Japan Foundation, Stockholm, Sweden, 2009\\%
  Scholarship for Studies in Japan, Japan Students Services Organization, Sendai, Japan, 2009%
\end{rsection}

\end{document}
